### 2023-05-05 paper-one/paper-one.tex
Fixing epub builds
- fixing epub title and series in both epub scripts
- fixed references section order in paper-two.tex (`section` within bibilography was causing errors)
- fixed svg resize errors by putting SVGs in their own directory... I have no idea why `epub-convert` was looking at the SVGs since the .tex file doesn't even reference them, but whatever.
- added a refrences section title to paper one
- adding graphicsmagick to readme (may not be required but it can't hurt)
Complete Linux build - remove polyglossia, use fontspec directly
* fonts are included inline now
* debs listed in READ

\usepackage{polyglossia}
\setdefaultlanguage{english}
\setotherlanguage{sanskrit}
\usepackage{fontspec}
\newfontfamily\devanagarifont[Scale=MatchUppercase]{Kohinoor Devanagari}

@@

The notion represented by the Pali word \textit{Saṅkhāra} can be split into two camps, in terms of its definition and use. The first, the notion that the body and mind contain ``impurities'' and that the objective of meditation is to rid the body-mind of such impurities, will be excluded from all discussion here. The second, more common use of the term ``Sankhara'' refers to ``conditioned phenomena'' or ``psychological dispositions''. The equivalent Hindi/Sanskrit word, \foreignlanguage{sanskrit}{संस्कार} (sanskaar) roughly translates in this context to ``mental impression''. This second definition will apply to this paper.

@@

\begin{thebibliography}{9}
\raggedright

>>>>

\usepackage{fontspec}
\newfontfamily\devanagarifontsans{NotoSansDevanagari-Regular.ttf}[
  BoldFont = NotoSansDevanagari-Bold.ttf ]
\newfontfamily\devanagarifontserif{NotoSerifDevanagari-Regular.ttf}[
  BoldFont = NotoSerifDevanagari-Bold.ttf ]

@@

The notion represented by the Pali word \textit{Saṅkhāra} can be split into two camps, in terms of its definition and use. The first, the notion that the body and mind contain ``impurities'' and that the objective of meditation is to rid the body-mind of such impurities, will be excluded from all discussion here. The second, more common use of the term ``Sankhara'' refers to ``conditioned phenomena'' or ``psychological dispositions''.
The equivalent Hindi/Sanskrit word, {\devanagarifontserif संस्कार} (sanskaar) roughly translates in this context to ``mental impression''. This second definition will apply to this paper.

@@

\section*{References}

\begin{thebibliography}{99}
\raggedright
